Loan word maps

### 2025-03-20 analysis/paper/paper.qmd
paper and data update

institute:
  - uhh:
      name: Universität Hamburg
      address: 23 Science Street, Eureka, Mississippi, USA
  - fi: Frobenius Institute
title-block-published: "Last updated"  
date: now
date-format: long
format: 
  docx:
    reference-doc: "../templates/template.docx" # Insert path for the DOCX file
execute:
  echo: true
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 600
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

Save an html version of all objects
```{r}
#| label: save-maps
#| eval: false
save_maps(data_list, background = "bw")
```

>>>>

institute:
  - uhh:
      name: Universität Hamburg
      address: 23 Science Street, Eureka, Mississippi, USA
  - fi: Frobenius Institute
title-block-published: "Last updated"  
date: now
date-format: long
format: 
  docx:
    reference-doc: "../templates/template.docx" # Insert path for the DOCX file
execute:
  echo: true
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 600
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
prefer-html: true
---

@@

```{r}
#| label: fonio
#| fig-cap: "fonio word forms"
create_leaflet_map(data_list[[2]])
```

Save an html version of all objects
```{r}
#| label: save-maps
#| eval: false
save_maps(data_list, background = "bw")

create_leaflet_map(data_list[[2]])
```
